Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-11-02 manuscript.tex

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are scalar inferences default inferences, in the sense that they arise
  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
  Levinson, 2000)?
\item
  Are scalar inferences default inferences, in the sense that they are
  computed automatically in online processing and only cancelled by
  context in a second effortful step if required by context (Bott \&
  Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
  et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
  2013; Tomlinson et al., 2013)?
\item
  What are the (linguistic and extra-linguistic) factors that affect
  whether a scalar implicature is derived (Bergen \& Grodner, 2012;
  Bonnefon et al., 2009; Breheny et al., 2013, 2006; Chemla \& Spector,
  2011; De Neys \& Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014;
  Degen \& Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts,
  Lassiter, Levy, \& Frank, 2015; Zondervan, 2010)?
\item
  How much diversity is there across implicature types, and within
  scalar implicatures across scale types, in whether or not an
  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
  van Tiel et al., 2016)?
\item
  At what age do children acquire the ability to compute implicatures
  (Barner et al., 2011; Horowitz, Schneider, \& Frank, 2017; Katsos \&
  Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou,
  2004; Stiller, Goodman, \& Frank, 2015)?
\end{enumerate}

@@

\change{Using the rate of \enquote{FALSE} responses in true but underinformative trials as a proxy for implicature calculation is relatively common in experimental pragmatics. For example, in the first study to investigate scalar implicatures experimentally, Noveck (2001) tested adults' and children's interpretations of the scalar items \emph{might} and \emph{some}. The dependent measure in Noveck (2001) was the rate of ``logically correct responses'', i.e. responding ``yes'' to statements such as \emph{Some giraffes have long necks} or \emph{There might be a parrot [in the box]} when there had to be a parrot in the box. He found that children show a higher rate of logically correct responses than adults, and concluded that children interpret scalar items \emph{some} and \emph{might} more logically (i.e. literally). Similarly in another landmark study, Papafragou and Musolino (2003) tested children and adults interpretation of the following set of scalar items: <\emph{two}, \emph{three}>, <\emph{some}, \emph{all}>, and <\emph{finish}, \emph{start}>. The dependent measure in this study was ``the proportion of \emph{No} responses to the puppet's [underinformative] statement''. The study concluded that ``while adults overwhelmingly rejected infelicitous descriptions, children almost never did so''. Furthermore, the study compared the implicature rates across scales and concluded that ``children also differed from from adults in that their rejection rate on the numerical scale was reliably higher than on the two other scales.'' In their final experiment, Papafragou and Musolino (2003) modified their task to invite scalar inferences more easily. They reported that this manipulation resulted in a significantly higher rejection rates. Based on these results, they concluded that children's ability to compute implicatures is affected by the type of scalar item as well as children's awareness of the task's goals. Since these early pioneering studies, many other studies have used the rate of false responses in underinformative trials as their dependent measure including Doran et al (2012), van Tiel et al (2016), Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), to name a few.}

@@

Our primary goal in this study was to test whether the estimated
implicature rate in the experimental task is affected by the linking
hypothesis and the number of response options available to participants.
To this end, we only analyzed the critical trials (exhaustive and
scalar). In particular, we classified each data point from critical
trials as constituting an implicature (1) or not (0) under the Strong
and Weak link. Figure \ref{fig:implicatureRatePlot} shows the resulting
implicature rates by condition and link. \change{It is immediately obvious that there is variability in inferred implicature rate. In particular, the Weak link appears to result in greater estimates of
implicature rates in tasks with four or five response options, compared to the Strong link. For the binary and ternary task, the assumed link appears to play a much smaller role.}

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are scalar inferences default inferences, in the sense that they arise
  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
  Levinson, 2000)?
\item
  Are scalar inferences default inferences, in the sense that they are
  computed automatically in online processing and only cancelled in a second effortful step if required by context (Bott \&
  Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
  et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
  2013; Tomlinson et al., 2013)?
\item
  What are the (linguistic and extra-linguistic) factors that affect
  whether a scalar implicature is derived (Bergen \& Grodner, 2012;
  Bonnefon et al., 2009; Breheny et al., 2013, 2006; Chemla \& Spector,
  2011; De Neys \& Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014;
  Degen \& Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts,
  Lassiter, Levy, \& Frank, 2015; Zondervan, 2010)?
\item
  How much diversity is there across implicature types, and within
  scalar implicatures across scale types, in whether or not an
  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
  van Tiel et al., 2016)?
\item
  At what age do children acquire the ability to compute implicatures
  (Barner et al., 2011; Horowitz, Schneider, \& Frank, 2017; Katsos \&
  Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou,
  2004; Stiller, Goodman, \& Frank, 2015)?
\end{enumerate}

@@

\change{Using the proportion of \enquote{FALSE} responses on true but underinformative trials as a proxy for implicature rate is  common in experimental pragmatics. For example, in one of the first studies to investigate scalar implicatures experimentally, Noveck (2001) tested adults' and children's interpretations of the scalar items \emph{might} and \emph{some}. The dependent measure in Noveck (2001) was the rate of ``logically correct responses'', i.e. responding ``yes'' to statements such as \emph{Some giraffes have long necks} or \emph{There might be a parrot [in the box]} when there had to be a parrot in the box. He found that children responded ``yes'' more frequently than adults, and concluded that children interpret scalar items \emph{some} and \emph{might} more logically (i.e. literally). Similarly in another landmark study, Papafragou and Musolino (2003) tested children and adults interpretation of the following set of scalar items: <\emph{two}, \emph{three}>, <\emph{some}, \emph{all}>, and <\emph{finish}, \emph{start}>. The dependent measure in this study was the proportion of ``No'' responses to a puppet's underinformative] statement. The study concluded that ``while adults overwhelmingly rejected infelicitous descriptions, children almost never did so''. Furthermore, the study compared  implicature rates across scales and concluded that ``children also differed from from adults in that their rejection rate on the numerical scale was reliably higher than on the two other scales.'' In their final experiment, Papafragou and Musolino (2003) modified their task to invite scalar inferences more easily. They reported that this manipulation resulted in a significantly higher rejection rates. Based on these results, they concluded that children's ability to compute implicatures is affected by the type of scalar item as well as children's awareness of the task's goals. Since these early pioneering studies, the rate of ``FALSE'' (or ``No'', ``Wrong'', ``Disagree'') responses on underinformative trials in truth-value judgment tasks has become a commonplace dependent measure (Doran et al (2012),  Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), inter alia.)}

@@

Our primary goal in this study was to test whether the estimated
implicature rate in the experimental task is affected by the linking
hypothesis and the number of response options available to participants.
To this end, we only analyzed the critical trials (exhaustive and
scalar). In particular, we classified each data point from critical
trials as constituting an implicature (1) or not (0) under the Strong
and Weak link. Figure \ref{fig:implicatureRatePlot} shows the resulting
implicature rates by condition and link. \change{It is immediately apparent that there is variability in inferred implicature rate. In particular, the Weak link appears to result in greater estimates of
implicature rates in tasks with four or five response options, compared to the Strong link. For the binary and ternary task, the assumed link appears to play a much smaller role.}
